---
title: "report"
author: "Monica Thieu"
date: "3/27/2020"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(magrittr)
library(rlang)
load(here::here("ignore", "data_R", "raw.rda"))
load(here::here("ignore", "data_R", "boots.rda"))
load(here::here("ignore", "data_R","preplots_rstanarm.rda"))
load(here::here("ignore", "data_R","preplots_rt_rstanarm.rda"))
load(here::here("ignore", "data_R", "aprime_by_ppm.rda"))

this_theme <- function (...) {
  
  out <- theme_bw() +
    theme(plot.title.position = "plot",
          axis.title = element_text(size = rel(1.2)),
          axis.text = element_text(size = rel(1)),
          strip.text = element_text(size = rel(1))) +
    theme(...)
  
  return (out)
}

signif_digits <- 3L
colors_exptCond <- c("#FF1926", "#0088c7")
colors_exptCond_probe <- c("#ff1926", "#0088c7", "#ff9ea3",  "#2ebdff")
```

# Da plotz

03/27/2020: Redo the aprime ppm boot plot with un-adjusted, not the added variable plot, but keep the multiple regression boot stuff for text reporting. Also re-run the boots for more iterations to stabilize the standard error estimates

Done: FIX WHAT YOU HAVE IN THE GLUE CALL TO REPORT THE CORRECT STD ERROR

04/03/2020: Move forward with the unadjusted aprime x ppm plot, beautify it accordingly and possibly??? add significance visual highlight

```{r major-plot-aprime-ppm-boot}
x <- aprime_by_ppm_boot %>%
  select(iteration, exptCond, probe, data_raw) %>%
  unnest(data_raw) %>%
  mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
  group_by(exptCond, probe, obs, ppm_diff, aprime_diff, aprime_diff_fit) %>%
  summarize(boot_median = median(predicted),
            boot_q025 = quantile(predicted, .025),
            boot_q975 = quantile(predicted, .975)) %>%
  mutate(rel_room = if_else(exptCond == "similar" & probe == "room", TRUE, FALSE)) %>%
  ggplot(aes(x = ppm_diff, y = aprime_diff,
             color = interaction(exptCond, probe),
             fill = interaction(exptCond, probe))) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", formula = y ~ x, size = 1, alpha = 0.3) +
  geom_text(aes(label = this_label),
            data = crossing(ppm_diff = 7.5, aprime_diff = -.18,
                            exptCond = c("identical", "similar"), probe = c("art", "room")) %>%
              mutate(this_label = if_else(exptCond == "similar" & probe == "room", "*", "")),
            size = 10, color = "black") +
  scale_color_manual(values = colors_exptCond_probe) +
  scale_fill_manual(values = colors_exptCond_probe) +
  facet_grid(probe ~ exptCond) +
  guides(color = FALSE, fill = FALSE) +
  labs(x = "CO ppm difference (ON smoking - OFF smoking)",
       y = "A' difference (ON smoking - OFF smoking)") +
  this_theme()

x

x %>%
  ggsave(filename = "ignore/figures/major_plot_aprime_by_ppm_grid_all.png",
       plot = .,
       device = "png",
       width = 6,
       height = 6,
       units = "in")

(x + theme(panel.grid = element_blank())) %>%
  ggsave(filename = "ignore/figures/major_plot_aprime_by_ppm_grid_none.png",
       plot = .,
       device = "png",
       width = 6,
       height = 6,
       units = "in")

(x + theme(panel.grid.minor = element_blank())) %>%
  ggsave(filename = "ignore/figures/major_plot_aprime_by_ppm_grid_minimal.png",
       plot = .,
       device = "png",
       width = 6,
       height = 6,
       units = "in")
```

```{r minor-plot-aprime-ppm-resid-boot}
aprime_by_ppm_boot %>%
  select(iteration, exptCond, probe, data_raw) %>%
  unnest(data_raw) %>%
  group_by(exptCond, probe, obs, ppm_diff_resid, aprime_diff_resid, aprime_diff_fit_resid) %>%
  summarize(boot_median = median(predicted),
            boot_q025 = quantile(predicted, .025),
            boot_q975 = quantile(predicted, .975)) %>%
  mutate(rel_room = if_else(exptCond == "relational" & probe == "room", TRUE, FALSE)) %>%
  ggplot(aes(x = ppm_diff_resid, y = aprime_diff_resid, color = rel_room, fill = rel_room)) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = boot_q025, ymax = boot_q975), color = FALSE, alpha = 0.3) +
  geom_line(aes(y = aprime_diff_fit_resid), size = 1) +
  geom_text(aes(label = glue::glue("beta = {estimate_raw}\n95% boot int = [{boot_q025}, {boot_q975}]")),
            data = aprime_by_ppm_boot %>%
              mutate(coefs = map2(coefs, coefs_raw, ~full_join(.x, .y, by = "term"))) %>%
              select(iteration, exptCond, probe, coefs) %>%
              unnest(coefs) %>%
              group_by(exptCond, probe, term, estimate_raw) %>%
              summarize(boot_median = median(estimate),
                        boot_mean = mean(estimate),
                        boot_q025 = quantile(estimate, .025),
                        boot_q975 = quantile(estimate, .975)) %>%
              mutate_if(is.numeric, signif, digits = signif_digits) %>%
              filter(term == "ppm_diff") %>%
              mutate(rel_room = if_else(exptCond == "relational" & probe == "room", TRUE, FALSE)),
            x = 9, y = -0.5, hjust = 1) +
  # geom_smooth(method = "lm", fill = "blue") +
  facet_grid(probe ~ exptCond) +
  guides(color = FALSE, fill = FALSE) +
  labs(x = "ppm_diff | aprime_off",
       y = "aprime_diff | aprime_off",
       title = "added variable plot of ppm_diff") +
  theme_bw()
```

03/27/2020: Investigate this graph... what is up with the bootstrap error distributions not being centered on the raw values

Update 03/31/2020: Refer to relevant exploratory graphs in the analysis document. Basically, the people with shitty off-smoking A' and a huge improvement in A', AND the people with great off-smoking A' and a huge reduction in A', are more likely to get bootstrap-resampled with relatively extreme values, driving the center of the bootstrap distribution of the A' off predictor higher. Additionally, intercepts and A' off slopes are correlated in the bootstrap distribution because the convergence point of the lines is above chance A'.

```{r minor-plot-aprime-ppm-coefplot-boot}
aprime_by_ppm_boot %>%
  mutate(coefs = map2(coefs, coefs_raw, ~full_join(.x, .y, by = "term"))) %>%
  select(iteration, exptCond, probe, coefs) %>%
  unnest(coefs) %>%
  mutate(term = recode_factor(term,
                              `(Intercept)` = "Intercept",
                              aprime_off_c = "A' OFF smoking",
                              ppm_diff = "ON - OFF change in CO ppm")) %>%
  group_by(exptCond, probe, term, estimate_raw) %>%
  summarize(boot_median = median(estimate),
            boot_mean = mean(estimate),
            boot_q025 = quantile(estimate, .025),
            boot_q25 = quantile(estimate, .25),
            boot_q75 = quantile(estimate, .75),
            boot_q975 = quantile(estimate, .975)) %>%
  ggplot(aes(x = boot_median, y = "term")) +
  geom_vline(xintercept = 0, linetype = 3) +
  geom_errorbarh(aes(xmin = boot_q025, xmax = boot_q975), height = 0) +
  geom_errorbarh(aes(xmin = boot_q25, xmax = boot_q75), height = 0, size = 1) +
  geom_point() +
  geom_point(aes(x = boot_mean), color = "purple") +
  geom_point(aes(x = estimate_raw), color = "hotpink") +
  facet_grid(exptCond + probe ~ term, scales = "free_x") +
  labs(x = "coefficient (unit effect on ON-OFF A' difference)",
       y = "model term",
       title = "model: A' diff ~ A' off (center = 0.5) + ppm diff (raw units)") +
  theme_bw()
```

```{r minor-plot-2x2x2-coefs}
x <- preplots_params %>%
  filter(startsWith(name, "full")) %>%
  unnest(iterations) %>%
  mutate(term = recode_factor(term,
                              intercept = "intercept",
                              corResp = "match present?",
                              exptCond = "condition",
                              probe = "attentional state",
                              on_smoking = "smoking status",
                              `corResp:exptCond` = "match present? x condition",
                              `corResp:probe` = "match present? x attention",
                              `corResp:on_smoking` = "match present? x smoking",
                              `probe:exptCond` = " condition x attention",
                              `on_smoking:exptCond` = "condition x smoking",
                              `probe:on_smoking` = "attention x smoking",
                              `corResp:probe:exptCond` = "match present? x condition x attention",
                              `corResp:on_smoking:exptCond` = "match present? x condition x smoking",
                              `corResp:probe:on_smoking` = "match present? x attention x smoking",
                              `probe:on_smoking:exptCond` = "condition x attention x smoking")) %>%
  group_by(term) %>%
  summarize(est_median = median(estimate),
            est_q025 = quantile(estimate, .025),
            est_q25 = quantile(estimate, .25),
            est_q75 = quantile(estimate, .75),
            est_q975 = quantile(estimate, .975)) %>%
  ggplot(aes(x = est_median, y = fct_rev(term))) +
  geom_vline(xintercept = 0, linetype = 3) +
  geom_errorbarh(aes(xmin = est_q025, xmax = est_q975), height = 0) +
  # geom_errorbarh(aes(xmin = est_q25, xmax = est_q75), size = 1, height = 0) +
  geom_point() +
  labs(x = "coefficient +- credible interval", y = NULL) +
  this_theme(plot.title.position = "panel")

x

x %>%
  ggsave("ignore/figures/minor_plot_2x2x2_coefs.png",
         plot = .,
         device = "png",
         width = 7,
         height = 4.5,
         units = "in")
```

03/27/2020: use the mean for the below plot. And add a figure b for this one omitting the raw data with sensibly truncated axes

red for control, blue for relational. lighter for art, darker for room. get Nick's illustrator CMYK codes for the conditions

04/03/2020: fix the color char vector to put the colors in the right order, also tweak opacity etc to get stuff to be darker

```{r major-plot-nick}
x <- preplots_raw_bysubj %>%
  filter(name == "raw") %>%
  mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
  ggplot(aes(x = on_smoking, y = aprime, color = interaction(exptCond, probe), fill = interaction(exptCond, probe))) +
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  geom_ribbon(aes(y = aprime_mean, ymin = aprime_q025, ymax = aprime_q975, group = 1),
              data = preplots_fixef %>%
              filter(name == "full") %>%
                mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
              group_by(on_smoking, exptCond, probe) %>%
              summarize(aprime_mean = mean(aprime),
                        aprime_q025 = quantile(aprime, .025),
                        aprime_q975 = quantile(aprime, .975)),
              linetype = 0,
              alpha = 0.3) +
  geom_line(aes(group = 1),
            data = preplots_fixef %>%
              filter(name == "full") %>%
              mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
              group_by(on_smoking, exptCond, probe) %>%
              summarize(aprime = mean(aprime)),
            size = 1,
            alpha = 1) +
  geom_hline(yintercept = 0.5, linetype = 3) +
  scale_x_discrete(labels = c("off" = "OFF", "on" = "ON")) +
  scale_color_manual(values = colors_exptCond_probe) +
  scale_fill_manual(values = colors_exptCond_probe) +
  labs(x = "smoking session",
       y = "A'") +
  guides(color = FALSE, fill = FALSE) +
  facet_grid( ~ exptCond + probe) +
  this_theme()

x

x %>%
  ggsave(filename = "ignore/figures/major_plot_nick.png",
       plot = .,
       device = "png",
       width = 7,
       height = 4,
       units = "in")

(x + theme(panel.grid = element_blank())) %>%
  ggsave(filename = "ignore/figures/major_plot_nick_grid_none.png",
       plot = .,
       device = "png",
       width = 7,
       height = 4,
       units = "in")

(x + theme(panel.grid.minor = element_blank())) %>%
  ggsave(filename = "ignore/figures/major_plot_nick_grid_minimal.png",
       plot = .,
       device = "png",
       width = 7,
       height = 4,
       units = "in")
```

04/03/2020: Make another version of this plot with 95% ribbons instead of paired angel hair. Also tinker with the angel hair plot to make things more visible. Plus add manual color legend for dark vs light

```{r minor-plot-nick-truncated}
preplots_fixef %>%
  filter(name == "full") %>%
  nest(data = -iteration) %>%
  sample_n(300) %>%
  unnest(data) %>%
  mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
  ggplot(aes(x = on_smoking, y = aprime, color = interaction(exptCond, probe))) +
  geom_line(aes(group = interaction(iteration, probe)), alpha = 0.05) +
  geom_line(aes(group = probe),
            data = preplots_fixef %>%
              filter(name == "full") %>%
              mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
              group_by(on_smoking, exptCond, probe) %>%
              summarize(aprime = mean(aprime)),
            size = 1.5,
            alpha = 0.8) +
  scale_color_manual(values = colors_exptCond_probe) +
  labs(x = "Smoking session",
       y = "A'",
       title = "Figure Nb",
       subtitle = "putative cholinergic modulation of A'") +
  facet_grid( ~ exptCond) +
  this_theme()
```

```{r minor-plot-nick-truncated-ribbon}
x <- preplots_fixef %>%
  filter(name == "full") %>%
  mutate(exptCond = recode(exptCond, control = "identical", relational = "similar")) %>%
  group_by(on_smoking, exptCond, probe) %>%
              summarize(aprime_mean = mean(aprime),
                        aprime_q025 = quantile(aprime, .025),
                        aprime_q975 = quantile(aprime, .975)) %>%
  ggplot(aes(x = on_smoking, y = aprime_mean,
             color = interaction(exptCond, probe, sep = " "),
             fill = interaction(exptCond, probe, sep = " "))) +
  geom_ribbon(aes(ymin = aprime_q025, ymax = aprime_q975, group = probe),
              linetype = 0,
              alpha = 0.25) +
  geom_line(aes(group = probe),
            size = 1.5,
            alpha = 0.8) +
  # geom_text(aes(label = probe),
    #         data = crossing(on_smoking = 1.5,
      #                       exptCond = c("identical", "similar"), probe = c("art", "room")) %>%
        #       mutate(aprime_mean = case_when(exptCond == "identical" & probe == "room" ~ .88,
          #                                    exptCond == "identical" & probe == "art" ~ .86,
            #                                  exptCond == "similar" & probe == "room" ~ .9,
              #                                exptCond == "similar" & probe == "art" ~ .92)),
            # size = 6) +
  scale_color_manual(values = colors_exptCond_probe) +
  scale_fill_manual(values = colors_exptCond_probe) +
  # guides(color = FALSE, fill = FALSE) +
  labs(x = "smoking session",
       y = "A'",
       color = "trial type",
       fill = "trial type") +
  facet_grid( ~ exptCond) +
  this_theme()

x

x %>%
  ggsave(filename = "ignore/figures/minor_plot_nick_truncated.png",
       plot = .,
       device = "png",
       width = 5,
       height = 4,
       units = "in")

(x + theme(panel.grid = element_blank())) %>%
  ggsave(filename = "ignore/figures/minor_plot_nick_truncated_grid_none.png",
       plot = .,
       device = "png",
       width = 5,
       height = 4,
       units = "in")

(x + theme(panel.grid.minor = element_blank())) %>%
  ggsave(filename = "ignore/figures/minor_plot_nick_truncated_grid_minimal.png",
       plot = .,
       device = "png",
       width = 5,
       height = 4,
       units = "in")
```

# Da resultz

1. **minor result**: Report valid > invalid A' from `manip_check`
1. **major result**: describe various ctrl/rel room/art things
1. **major result**: describe on/off smoking differences
1. **minor result**: describe converging results from alternate model fits
1. **minor result**: relational on-off room-art A' interaction? from dummy model (introduce said model also)
1. **major result**: A' by ppm diffs bootstrap biznaz

04/03/2020:

- Harmonize terminology with what Nick is reporting in the patient manuscript returned for response to review
- report for all estimates, mean [q025, q975]
- report RT for `manip_check` analysis also
- generally, where appropriate, interleave RT results in with A' results. In general, do not break RT out by response accuracy, just by task conditions

## main copy-paste boy

```{r, echo = FALSE}
summarize_report <- function (data, col, ..., stat_name = "", unit_name = "", digs = signif_digits) {
  if (unit_name != "") unit_name %<>% paste0(" ", .)
  glue_in = if_else(stat_name != "",
                    "{stat_name} = {a}{unit_name}, 95% CI [{b}, {c}]",
                    "{a}{unit_name}, 95% CI [{b}, {c}]")
  
  col_chr = as_name(enexpr(col))
  group_cols = enexprs(...)
  
  data %<>%
    select(iteration, !!!group_cols, starts_with(col_chr)) %>%
    pivot_longer(cols = starts_with(col_chr),
                 names_to = "metric_type",
                 values_to = "value",
                 names_prefix = glue::glue("{col_chr}_"))
  
  if (!is.null(group_cols)) {
    data %<>% group_by(!!!group_cols, metric_type)
  } else {
    data %<>% group_by(metric_type)
  }
  data %<>%
    summarize(avg = mean(value),
              q025 = quantile(value, .025),
              q975 = quantile(value, .975)) %>% 
    mutate_at(c("avg", "q025", "q975"), signif, digits = digs) %>%
    mutate(txt_apa = pmap_chr(list(avg, q025, q975),
                              function (a, b, c) {glue::glue(glue_in)}
    )
    )
  
  return (data)
}

coefs <- preplots_params %>%
  unnest(iterations) %>%
  summarize_report(estimate, name, term, stat_name = "beta")

coefs_rt <- preplots_rt_params %>%
  unnest(iterations) %>%
  summarize_report(estimate, name, term, stat_name = "beta")

get_coefs <- function (model_name, model_term, these_coefs = coefs) {
  these_coefs %>%
    filter(name == model_name, term == model_term) %>%
    pull(txt_apa)
}
```

```{r, echo = FALSE}
aprimes_manip_check <- preplots_fixef %>%
  filter(name == "manip_check") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = valid, values_from = aprime, names_prefix = "aprime_") %>% 
  mutate(aprime_diff = aprime_1 - aprime_0) %>%
  summarize_report(aprime_diff, stat_name = "estimated A' difference")

aprimes_manip_check_exptCond <- preplots_fixef %>%
  filter(name == "manip_check") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = valid, values_from = aprime, names_prefix = "aprime_") %>% 
  mutate(aprime_diff = aprime_1 - aprime_0) %>%
  summarize_report(aprime_diff, exptCond, stat_name = "estimated A' difference")

rts_manip_check <- preplots_rt_fixef %>%
  filter(name == "manip_check") %>%
  pivot_wider(names_from = valid, values_from = ends_with("rt_pred")) %>% 
  mutate(rt_diff = rt_pred_1 - rt_pred_0) %>%
  summarize_report(rt_diff, stat_name = "estimated RT difference", unit_name = "msec")
```

_Valid vs. Invalid Trials._ We first examined whether our attentional manipulation was successful by comparing performance on valid vs. invalid trials. If attention is effectively engaged by the cue at the beginning of the trial (i.e., ‘ART’ or ‘ROOM’), then performance should be more accurate and faster when the probe matches the cue (i.e., valid trials) than when it does not (i.e., invalid trials; Posner, 1980). To that end, we used a Bayesian mixed model to examine performance across experimental conditions as a function of trial validity (valid vs. invalid trials). These analyses confirmed that participants were more accurate on valid vs. invalid trials, as indexed by a main effect of validity (`r get_coefs("manip_check", "corResp:valid")`; `r aprimes_manip_check$txt_apa`). We also found an interaction of validity and condition on accuracy such that participants showed a smaller valid vs. invalid boost in accuracy for identical trials relative to similar trials (`r get_coefs("manip_check", "corResp:valid:exptCond")`; identical trials: `r aprimes_manip_check_exptCond %>% filter(exptCond == "control") %>% pull(txt_apa)`; similar trials: `r aprimes_manip_check_exptCond %>% filter(exptCond == "relational") %>% pull(txt_apa)`). Furthermore, an analysis of log-transformed response times (RTs) confirmed that participants were faster on valid vs. invalid trials (`r get_coefs("manip_check", "valid", coefs_rt)`; `r rts_manip_check$txt_apa`).

Taken together, these results suggest that attention was effectively engaged by the cue at the beginning of the trial: Participants were more accurate and faster on valid vs. invalid trials. Having verified that participants modulated their attention based on trial instructions, we next focus analyses on valid trials.

```{r, echo = FALSE}
aprimes_2x2x2_exptCond <- preplots_fixef %>%
  filter(name == "full") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = exptCond, values_from = aprime) %>%
  mutate(aprime_diff = relational - control) %>%
  summarize_report(aprime_diff)

rts_2x2x2_exptCond <- preplots_rt_fixef %>%
  filter(name == "full") %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = exptCond, values_from = rt_pred) %>% 
  mutate(rt_diff = relational - control) %>%
  summarize_report(rt_diff,
                   stat_name = "estimated RT difference", unit_name = "msec")

aprimes_2x2x2_probe <- preplots_fixef %>%
  filter(name == "full") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = probe, values_from = aprime) %>%
  mutate(aprime_diff = room - art) %>%
  summarize_report(aprime_diff, stat_name = "estimated A' difference")

rts_2x2x2_probe <- preplots_rt_fixef %>%
  filter(name == "full") %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = probe, values_from = rt_pred) %>% 
  mutate(rt_diff = room - art) %>%
  summarize_report(rt_diff, stat_name = "estimated RT difference", unit_name = "msec")

aprimes_2x2x2_probe_exptCond <- preplots_fixef %>%
  filter(name == "full") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = c(exptCond, probe), values_from = aprime) %>%
  mutate(aprime_diff_ctrl = control_room - control_art,
         aprime_diff_rel = relational_room - relational_art,
         aprime_diff_probe_exptCond = aprime_diff_rel - aprime_diff_ctrl) %>%
  summarize_report(aprime_diff, stat_name = "estimated A' difference")

rts_2x2x2_probe_exptCond <- preplots_rt_fixef %>%
  filter(name == "full") %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = c(exptCond, probe), values_from = rt_pred) %>% 
  mutate(rt_diff_ctrl = control_room - control_art,
         rt_diff_rel = relational_room - relational_art,
         rt_diff_probe_exptCond = rt_diff_rel - rt_diff_ctrl) %>%
  summarize_report(rt_diff, stat_name = "estimated RT difference", unit_name = "msec")
```

**Figure N-1.** Coefficient estimates of the model for trialwise match detection performance. In this model, the main effect of `is_match` reflects the magnitude of behavioral sensitivity across all experimental conditions. Differences in sensitivity between experimental conditions are indexed by interaction terms between `is_match` and the other experimental conditions. Accordingly, predicted A' (shown below in Figure N) was generated from these coefficients by treating the posterior estimate of P("choose match" | is_match = present) as the hit rate, and P("choose match" | is_match = absent) as the false alarm rate, in the A' formula. Error bars = 95% credible intervals.

**Figure N.** Behavioral performance (A'). Overall, participants performed better on identical trials (left two panels, red) than similar trials (right two panels, blue). Points and faint lines indicate raw A' values for each participant. Heavy lines and error ribbons indicate group-level model-predicted A' +- 95% credible interval.  Dashed horizontal line indicates chance performance (A' = 0.5).

_Art vs. Room and Identical vs. Similar Trials._ We next examined how individuals performed across conditions (identical vs. similar trials) and attentional states (art vs. room) in a Bayesian mixed model predicting accuracy as a function of identical vs. similar condition, art vs. room attention type, and on vs. off smoking session. As expected, A’ was substantially higher on identical vs. similar trials, as indexed by a main effect of condition (`r get_coefs("full", "corResp:exptCond")`; estimated A' difference = `r -aprimes_2x2x2_exptCond$avg`, 95% CI [`r -aprimes_2x2x2_exptCond$q975`, `r -aprimes_2x2x2_exptCond$q025`]). We did not find a comparable main effect of condition on log-RTs (`r get_coefs("full", "exptCond", coefs_rt)`; `r rts_2x2x2_exptCond$txt_apa`).

In contrast, performance was not meaningfully different between art and room attentional states, neither for A’ (`r get_coefs("full", "corResp:probe")`; `r aprimes_2x2x2_probe$txt_apa`) nor for log-RTs (`r get_coefs("full", "corResp:probe", coefs_rt)`; `r rts_2x2x2_probe$txt_apa`).

However, for A’, there was an interaction between condition and attentional state, `r get_coefs("full", "corResp:probe:exptCond")`. A’ on identical trials was higher for room vs. art attention (`r aprimes_2x2x2_probe_exptCond %>% filter(metric_type == "ctrl") %>% pull(txt_apa)`), but A’ on similar trials did not meaningfully differ between room vs. art attention (`r aprimes_2x2x2_probe_exptCond %>% filter(metric_type == "rel") %>% pull(txt_apa)`). There was no such interaction for log-RTs, (`r get_coefs("full", "probe:exptCond", coefs_rt)`).

```{r, echo = FALSE}
aprimes_2x2x2_smoking <- preplots_fixef %>%
  filter(name == "full") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = on_smoking, values_from = aprime) %>%
  mutate(aprime_diff = on - off) %>%
  summarize_report(aprime_diff, stat_name = "estimated A' difference")

rts_2x2x2_smoking <- preplots_rt_fixef %>%
  filter(name == "full") %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = on_smoking, values_from = rt_pred) %>% 
  mutate(rt_diff = on - off) %>%
  summarize_report(rt_diff, stat_name = "estimated RT difference", unit_name = "msec")

aprimes_2x2x2_smoking_simple <- preplots_fixef %>%
  filter(name == "full") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = on_smoking, values_from = aprime) %>%
  mutate(aprime_diff = on - off) %>%
  summarize_report(aprime_diff, exptCond, probe)

aprimes_smoking_exptCond <- preplots_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = c(on_smoking, exptCond), values_from = aprime) %>%
  mutate(aprime_diff_ctrl = on_control - off_control,
         aprime_diff_rel = on_relational - off_relational,
         aprime_diff_smoking_exptCond = aprime_diff_rel - aprime_diff_ctrl) %>%
  summarize_report(aprime_diff, name, stat_name = "estimated A' difference")

aprimes_smoking_probe <- preplots_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = c(on_smoking, probe), values_from = aprime) %>%
  mutate(aprime_diff_room = on_room - off_room,
         aprime_diff_art = on_art - off_art,
         aprime_diff_smoking_probe = aprime_diff_room - aprime_diff_art) %>%
  summarize_report(aprime_diff, name, stat_name = "estimated A' difference")

aprimes_smoking_exptCond_probe <- preplots_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = c(on_smoking, exptCond, probe), values_from = aprime) %>%
  mutate(aprime_diff_ctrl_room = on_control_room - off_control_room,
         aprime_diff_ctrl_art = on_control_art - off_control_art,
         aprime_diff_rel_room = on_relational_room - off_relational_room,
         aprime_diff_rel_art = on_relational_art - off_relational_art,
         aprime_diff_ctrl_probe = aprime_diff_ctrl_room - aprime_diff_ctrl_art,
         aprime_diff_rel_probe = aprime_diff_rel_room - aprime_diff_rel_art,
         aprime_diff_exptCond_probe = aprime_diff_rel_probe - aprime_diff_rel_art) %>%
  summarize_report(aprime_diff, name, stat_name = "estimated A' difference")

rts_smoking_exptCond <- preplots_rt_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = c(on_smoking, exptCond), values_from = rt_pred) %>%
  mutate(rt_diff_ctrl = on_control - off_control,
         rt_diff_rel = on_relational - off_relational,
         rt_diff_smoking_exptCond = rt_diff_rel - rt_diff_ctrl) %>%
  summarize_report(rt_diff, name, stat_name = "estimated RT difference", unit_name = "msec")

rts_smoking_probe <- preplots_rt_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = c(on_smoking, probe), values_from = rt_pred) %>%
  mutate(rt_diff_room = on_room - off_room,
         rt_diff_art = on_art - off_art,
         rt_diff_smoking_probe = rt_diff_room - rt_diff_art) %>%
  summarize_report(rt_diff, name, stat_name = "estimated RT difference", unit_name = "msec")

rts_smoking_exptCond_probe <- preplots_rt_fixef %>%
  filter(name != "manip_check") %>%
  mutate(name = case_when(name %in% c("dummy_art", "dummy_room") ~ "dummy_attn",
                          startsWith(name, "sep") ~ "sep",
                          TRUE ~ name)) %>%
  select(-log_rt_pred) %>%
  pivot_wider(names_from = c(on_smoking, exptCond, probe), values_from = rt_pred) %>%
  mutate(rt_diff_ctrl_room = on_control_room - off_control_room,
         rt_diff_ctrl_art = on_control_art - off_control_art,
         rt_diff_rel_room = on_relational_room - off_relational_room,
         rt_diff_rel_art = on_relational_art - off_relational_art,
         rt_diff_ctrl_probe = rt_diff_ctrl_room - rt_diff_ctrl_art,
         rt_diff_rel_probe = rt_diff_rel_room - rt_diff_rel_art,
         rt_diff_exptCond_probe = rt_diff_rel_probe - rt_diff_rel_art) %>%
  summarize_report(rt_diff, name, stat_name = "estimated RT difference", unit_name = "msec")
```

_Comparison of ON vs OFF smoking sessions._ We then turned to how performance on these tasks might be modulated by nicotine. We did not find a main effect of smoking session on A’, (`r get_coefs("full", "corResp:on_smoking")`; `r aprimes_2x2x2_smoking$txt_apa`), suggesting that across trial types, A’ was not consistently higher during the ON session than the OFF session.

We also did not find a main effect of smoking session on log-RTs (`r get_coefs("full", "on_smoking", coefs_rt)`; `r rts_2x2x2_smoking$txt_apa`).

Next, we interrogated task-dependent effects of nicotine on performance. Because we initially hypothesized that nicotine would preferentially improve performance on similar room trials, we also examined two-way interactions between smoking session and condition (identical vs. similar) and smoking session and attentional state (art vs. room) on performance. We did not find a two-way interaction effect of smoking session and condition on A’ (`r get_coefs("full", "corResp:on_smoking:exptCond")`) or RT (`r get_coefs("full", "on_smoking:exptCond", coefs_rt)`), nor did we find a two-way interaction effect of smoking session and attentional state on A’ (`r get_coefs("full", "corResp:probe:on_smoking")`) or RT (`r get_coefs("full", "probe:on_smoking", coefs_rt)`).


```{r, echo = FALSE}
coefs_aprime_by_ppm <- aprime_by_ppm_boot %>%
  mutate(coefs = map2(coefs, coefs_raw, ~full_join(.x, .y, by = "term"))) %>%
  select(iteration, exptCond, probe, coefs) %>%
  unnest(coefs) %>%
  rename(raw = "estimate_raw") %>%
  filter(term == "ppm_diff") %>%
  summarize_report(estimate, exptCond, probe, raw, stat_name = "beta", unit_name = "ppm units") %>%
  ungroup() %>%
  mutate(raw = signif(raw, digits = signif_digits),
         txt_apa_2 = glue::glue("beta = {raw} ppm units, bootstrapped 95% CI [{q025}, {q975}]"))

pcor_aprime_by_ppm <- aprime_by_ppm_boot %>%
  select(iteration, exptCond, probe, starts_with("resid")) %>%
  unnest(c(resid_aprime_diff, resid_ppm_diff)) %>%
  group_by(iteration, exptCond, probe) %>%
  summarize(pcor = cor(aprime_diff_resid, ppm_diff_resid)) %>%
  summarize_report(pcor, exptCond, probe, stat_name = "partial Pearson correlation") %>%
  mutate(txt_apa_2 = glue::glue("partial Pearson correlation = {avg}, bootstrapped 95% CI [{q025}, {q975}]"))

# at approx q925 this stuff starts to pop out. not q975
pcor_diff_aprime_by_ppm <- aprime_by_ppm_boot %>%
  select(iteration, exptCond, probe, starts_with("resid")) %>%
  unnest(c(resid_aprime_diff, resid_ppm_diff)) %>%
  group_by(iteration, exptCond, probe) %>%
  summarize(pcor = cor(aprime_diff_resid, ppm_diff_resid)) %>%
  pivot_wider(names_from = c(exptCond, probe), values_from = pcor) %>%
  mutate(pcor_diff_sa = relational_art - relational_room,
         pcor_diff_ia = control_art - relational_room,
         pcor_diff_ir = control_room - relational_room) %>%
  summarize_report(pcor_diff, stat_name = "partial Pearson's r difference")
```

_Supplementary Models of Performance._ ONLY UPDATED IN THE GOOGLE DOC.

_Individual Differences._ The above analyses treat smoking as a binary variable: they simply compared the ON and OFF smoking sessions. However, more precise information is available about individuals’ smoking, because for each session we obtained measures of carbon monoxide (CO) parts-per-million (ppm). This tells us how recently or how much an individual smoked, allowing us to investigate possible dose-dependent effects of smoking nicotine. If nicotine smoking enhances attentional performance, then the individuals who show the greatest CO ppm difference (in the ON vs. OFF smoking session) should show the greatest performance enhancements (in the ON vs. OFF smoking session). To investigate this, we ran four independent, between-participants linear regressions predicting A’ difference as a function of CO ppm difference (ON vs. OFF), with one regression for each task: identical art, identical room, similar art, and similar room.

**Figure N+1.** Dose-dependent effects of nicotine on behavioral sensitivity (A'). On similar room trials (bottom right), participants who showed a greater increase in CO ppm from the OFF to the ON smoking session showed larger increases in A' from the OFF to the ON smoking session. Participants did not show such an effect for identical art, identical room, or similar art trials. Within each panel, each point represents one subject; each subject appears in all four panels. * bootstrapped p < .05.

Indeed, we found a modest positive correlation between these measures for the similar room task (`r coefs_aprime_by_ppm %>% filter(exptCond == "relational", probe == "room") %>% pull(txt_apa_2)`; `r pcor_aprime_by_ppm %>% filter(exptCond == "relational", probe == "room") %>% pull(txt_apa_2)`), such that a CO increase of 1 ppm from OFF to ON smoking predicted a `r coefs_aprime_by_ppm %>% filter(exptCond == "relational", probe == "room") %>% pull(raw)` unit increase in A’ from OFF to ON smoking. CO ppm differences did not predict performance enhancements on any other trial type (identical art: `r coefs_aprime_by_ppm %>% filter(exptCond == "control", probe == "art") %>% pull(txt_apa_2)`; identical room: `r coefs_aprime_by_ppm %>% filter(exptCond == "control", probe == "room") %>% pull(txt_apa_2)`; similar art: `r coefs_aprime_by_ppm %>% filter(exptCond == "relational", probe == "art") %>% pull(txt_apa_2)`). Direct comparison showed that the partial Pearson correlation between CO ppm difference and A’ difference ON - OFF smoking for similar room trials was marginally higher than than the partial Pearson correlations for the other three trial types (similar room > identical art: `r pcor_diff_aprime_by_ppm %>% filter(metric_type == "ia") %>% pull(txt_apa)`; similar room > identical room: `r pcor_diff_aprime_by_ppm %>% filter(metric_type == "ir") %>% pull(txt_apa)`; similar room > similar art: `r pcor_diff_aprime_by_ppm %>% filter(metric_type == "sa") %>% pull(txt_apa)`).  

## describe converging results from alternate model fits

REMOVED, now only being updated in the Google Doc

```{r, echo = FALSE}
# relational on-off room-art A' interaction? from dummy model
# NOT REPORTING
aprimes_dummy_smoking <- preplots_fixef %>%
  filter(name == "dummy_all") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = on_smoking, values_from = aprime) %>%
  mutate(aprime_diff = on - off) %>%
  summarize_report(aprime_diff, exptCond, probe)

aprimes_dummy_smoking_probe <- preplots_fixef %>%
  filter(name == "dummy_all") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = c(on_smoking, probe), values_from = aprime) %>%
  mutate(aprime_diff_room = on_room - off_room,
         aprime_diff_art = on_art - off_art,
         aprime_diff_smoking_probe = aprime_diff_room - aprime_diff_art) %>%
  summarize_report(aprime_diff, exptCond)
```


### model fit

Should be moved to the statistical methods section but the code will stay here for now just in case

```{r, echo = FALSE}
errors <- preplots_raw_bysubj %>%
  select(-valid) %>%
  nest(data = -name) %>%
  mutate(raw = data[name == "raw"]) %>%
  filter(name != "raw") %>%
  mutate(data = map2(data, raw,
                     ~full_join(.x, .y, by = c("subj_num", "on_smoking", "exptCond", "probe"), suffix = c("_model", "_raw")))) %>%
  select(-raw) %>%
  unnest(data) %>%
  pivot_longer(cols = c(ends_with("model"), ends_with("raw")), names_to = c("metric_type", ".value"), names_pattern = "(.*)_(.*)") %>%
  mutate(error = model - raw) %>%
  group_by(name, metric_type, on_smoking, exptCond, probe) %>%
  summarize(rmse = sqrt(mean(error ^ 2)),
            mae = median(abs(error))) %>%
  pivot_longer(cols = c(rmse, mae), names_to = "error_type", values_to = "error")

errors_supp <- preplots_raw_bysubj %>%
  filter(name != "raw") %>%
  select(-valid) %>%
  nest(data = -name) %>%
  mutate(model_2x2x2 = data[name == "model_2x2x2"]) %>%
  filter(name != "model_2x2x2") %>%
  mutate(data = map2(data, model_2x2x2,
                     ~full_join(.x, .y, by = c("subj_num", "on_smoking", "exptCond", "probe"), suffix = c("_supp", "_full")))) %>%
  select(-model_2x2x2) %>%
  unnest(data) %>%
  pivot_longer(cols = c(ends_with("supp"), ends_with("full")), names_to = c("metric_type", ".value"), names_pattern = "(.*)_(.*)") %>%
  mutate(error = supp - full) %>%
  group_by(name, metric_type, on_smoking, exptCond, probe) %>%
  summarize(rmse = sqrt(mean(error ^ 2)),
            mae = median(abs(error))) %>%
  pivot_longer(cols = c(rmse, mae), names_to = "error_type", values_to = "error")
```

To assess model fit and validate subsequent inferences from the model, we used the model to generate each subject's posterior predicted A' in each task condition, and calculated the errors between predicted A' and raw A' for each subject x condition. We examined median absolute error, as median absolute error does not up-weight extremely large errors, as does root-mean-squared error. Median absolute error was below 0.05 A' units across subjects in seven of eight factorial task conditions.
