---
title: "report"
author: "Monica Thieu"
date: "3/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
load(here::here("ignore", "data_R", "raw.rda"))
load(here::here("ignore", "data_R", "boots.rda"))
load(here::here("ignore", "data_R","preplots_rstanarm.rda"))
load(here::here("ignore", "data_R", "aprime_by_ppm.rda"))
```

# Da plotz

03/27/2020: Redo the aprime ppm boot plot with un-adjusted, not the added variable plot, but keep the multiple regression boot stuff for text reporting. Also re-run the boots for more iterations to stabilize the standard error estimates

FIX WHAT YOU HAVE IN THE GLUE CALL TO REPORT THE CORRECT STD ERROR

```{r major-plot-aprime-ppm-resid-boot}
aprime_by_ppm_boot %>%
  select(iteration, exptCond, probe, data_raw) %>%
  unnest(data_raw) %>%
  group_by(exptCond, probe, obs, ppm_diff_resid, aprime_diff_resid, aprime_diff_fit) %>%
  summarize(boot_median = median(predicted),
            boot_q025 = quantile(predicted, .025),
            boot_q975 = quantile(predicted, .975)) %>%
  mutate(rel_room = if_else(exptCond == "relational" & probe == "room", TRUE, FALSE)) %>%
  ggplot(aes(x = ppm_diff_resid, y = aprime_diff_resid, color = rel_room, fill = rel_room)) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = boot_q025, ymax = boot_q975), color = FALSE, alpha = 0.3) +
  geom_line(aes(y = aprime_diff_fit), size = 1) +
  geom_text(aes(label = glue::glue("beta = {signif(estimate, 3)} +- boot SE = {round(std.error, 4)}")),
            data = aprime_by_ppm %>%
              mutate(coefs = map(model, broom::tidy)) %>%
              select(-data, -model) %>%
              unnest(coefs) %>%
              filter(term == "ppm_diff") %>%
              mutate(rel_room = if_else(exptCond == "relational" & probe == "room", TRUE, FALSE)),
            x = 8, y = -0.5, hjust = 1) +
  # geom_smooth(method = "lm", fill = "blue") +
  facet_grid(probe ~ exptCond) +
  guides(color = FALSE, fill = FALSE) +
  labs(x = "ppm_diff | aprime_off",
       y = "aprime_diff | aprime_off",
       title = "added variable plot of ppm_diff") +
  theme_bw()
```

03/27/2020: Investigate this graph... what is up with the bootstrap error distributions not being centered on the raw values

```{r minor-plot-aprime-ppm-coefplot-boot}
aprime_by_ppm_boot %>%
  mutate(coefs = map2(coefs, coefs_raw, ~full_join(.x, .y, by = "term"))) %>%
  select(iteration, exptCond, probe, coefs) %>%
  unnest(coefs) %>%
  mutate(term = recode_factor(term,
                              `(Intercept)` = "Intercept",
                              aprime_off_c = "A' OFF smoking",
                              ppm_diff = "ON - OFF change in CO ppm")) %>%
  group_by(exptCond, probe, term, estimate_raw) %>%
  summarize(boot_median = median(estimate),
            boot_mean = mean(estimate),
            boot_q025 = quantile(estimate, .025),
            boot_q25 = quantile(estimate, .25),
            boot_q75 = quantile(estimate, .75),
            boot_q975 = quantile(estimate, .975)) %>%
  ggplot(aes(x = boot_median, y = "term")) +
  geom_vline(xintercept = 0, linetype = 3) +
  geom_errorbarh(aes(xmin = boot_q025, xmax = boot_q975), height = 0) +
  geom_errorbarh(aes(xmin = boot_q25, xmax = boot_q75), height = 0, size = 1) +
  geom_point() +
  geom_point(aes(x = boot_mean), color = "purple") +
  geom_point(aes(x = estimate_raw), color = "hotpink") +
  facet_grid(exptCond + probe ~ term, scales = "free_x") +
  labs(x = "coefficient (unit effect on ON-OFF A' difference)",
       y = "model term",
       title = "model: A' diff ~ A' off (center = 0.5) + ppm diff (raw units)") +
  theme_bw()
```

```{r minor-plot-2x2x2-coefs}
preplots_params %>%
  filter(startsWith(name, "full")) %>%
  unnest(iterations) %>%
  mutate(term = recode_factor(term,
                              intercept = "intercept",
                              corResp = "match present?",
                              exptCond = "condition",
                              probe = "attention type",
                              on_smoking = "smoking status",
                              `corResp:exptCond` = "match present? x condition",
                              `corResp:probe` = "match present? x attention state",
                              `corResp:on_smoking` = "match present? x smoking status",
                              `probe:exptCond` = "trial type x attention state",
                              `on_smoking:exptCond` = "trial type x smoking status",
                              `probe:on_smoking` = "attention state x smoking status")) %>%
  group_by(term) %>%
  summarize(est_median = median(estimate),
            est_q025 = quantile(estimate, .025),
            est_q25 = quantile(estimate, .25),
            est_q75 = quantile(estimate, .75),
            est_q975 = quantile(estimate, .975)) %>%
  ggplot(aes(x = est_median, y = fct_rev(term))) +
  geom_vline(xintercept = 0, linetype = 3) +
  geom_errorbarh(aes(xmin = est_q025, xmax = est_q975), height = 0) +
  geom_errorbarh(aes(xmin = est_q25, xmax = est_q75), size = 1, height = 0) +
  geom_point() +
  labs(title = "visual coefficients/SEs for 2x2x2 model") +
  theme_bw()
```

03/27/2020: use the mean for the below plot. And add a figure b for this one omitting the raw data with sensibly truncated axes

red for control, blue for relational. lighter for art, darker for room. get Nick's illustrator CMYK codes for the conditions

```{r major-plot-nick}
preplots_raw_bysubj %>%
  filter(name == "raw") %>%
  ggplot(aes(x = on_smoking, y = aprime, color = exptCond)) +
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_jitter(width = 0.1, alpha = 0.2) +
  geom_line(aes(group = 1),
            data = preplots_raw_bysubj %>%
              filter(name == "model_2x2x2") %>%
              group_by(on_smoking, exptCond, probe) %>%
              summarize(aprime = mean(aprime)),
            size = 1.5,
            alpha = 0.8) +
  geom_hline(yintercept = 0.5, linetype = 3) +
  labs(x = "Smoking status",
       y = "A'",
       title = "Figure N",
       subtitle = "putative cholinergic modulation of A'") +
  facet_grid( ~ exptCond + probe) +
  theme_bw()
```

# Da resultz

- **minor result**: Report valid > invalid A' from `manip_check`
- **major result**: describe various ctrl/rel room/art things
- **major result**: describe on/off smoking differences
- **minor result**: describe converging results from alternate model fits
- **minor result**: relational on-off room-art A' interaction? from dummy model (introduce said model also)
- **major result**: A' by ppm diffs bootstrap biznaz

```{r}
coefs_manip_check <- preplots_params$iterations[[2]] %>%
  group_by(term) %>%
  summarize(est_mean = mean(estimate),
            est_sd = sd(estimate)) %>%
  mutate_if(is.numeric, signif, digits = 3)

aprimes_manip_check <- preplots_fixef %>%
  filter(name == "manip_check") %>%
  select(-starts_with("rate")) %>%
  pivot_wider(names_from = valid, values_from = aprime, names_prefix = "aprime_") %>% 
  mutate(aprime_diff = aprime_1 - aprime_0) %>%
  summarize(diff_mean = mean(aprime_diff), diff_sd = sd(aprime_diff)) %>%
  mutate_if(is.numeric, signif, digits = 3)
```

A supplementary model estimating memory performance as a function of valid/invalid attention probe type confirmed that participants answered more accurately on valid probed trials than invalid probed trials, beta = `r coefs_manip_check$est_mean[coefs_manip_check$term == "corResp:valid"]`, s.e. = `r coefs_manip_check$est_sd[coefs_manip_check$term == "corResp:valid"]`, corresponding to an estimated A' difference of `r aprimes_manip_check$diff_mean` +- `r aprimes_manip_check$diff_sd`.

```{r}

```

